### 2024-09-17 base-rates.qmd
20240916 - copyediting

Example 1: You just came home and a strange pair of underwear in your drawer.
What is the probability that your partner is cheating on you?

- the [prior probability](#sec-baseRate) that your spouse is cheating on you: 4%
- the [conditional probability](#sec-conditionalProbability) of underwear appearing given that your spouse is cheating on you: 50%
- the [conditional probability](#sec-conditionalProbability) of underwear appearing given that your spouse is *not* cheating on you: 5%

>>>>

Example 1: You came home and found a strange pair of underwear in your underwear drawer.
What is the probability that your partner is cheating on you?

- the [prior probability](#sec-baseRate) that your partner is cheating on you: 4%
- the [conditional probability](#sec-conditionalProbability) of underwear appearing given that your partner is cheating on you: 50%
- the [conditional probability](#sec-conditionalProbability) of underwear appearing given that your partner is *not* cheating on you: 5%
